%-------------------------
% Resume in LaTeX
% Author : Wanyama William Achuchi
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \textbf{#1} & #2 \\
  \textit{\small#3} & \textit{\small #4} 
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/DeveloperWilliams}{\Large Wanyama William Achuchi}} & Email: \href{mailto:archywilliams2@gmail.com}{archywilliams2@gmail.com}\\
  \href{https://github.com/DeveloperWilliams}{github.com/DeveloperWilliams} & Mobile: \href{tel:+254708966189}{+254-708-966189} \\
  & \href{https://www.linkedin.com/in/achuchi/}{linkedin.com/in/achuchi} \\
  & \href{https://x.com/Dev_Williee}{x.com/Dev\_Williee} \\
\end{tabular*}

%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
  \small{
    Fullstack developer with hands-on experience in MERN stack development. Proven ability to design, implement, and deploy full-stack applications, ranging from e-commerce platforms to dynamic content management systems. Focused on delivering clean, maintainable code and seamless user experiences. Strong communication and teamwork skills in agile environments. Adept at troubleshooting and optimizing both frontend and backend code, with a focus on improving system performance and user satisfaction.
  }

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{JavaScript, TypeScript, Python, HTML, CSS, SQL}
    \resumeSubItem{Frameworks}{React, Node.js, Express, Next.js}
    \resumeSubItem{Databases}{MongoDB, MySQL, PostgreSQL}
    \resumeSubItem{Tools}{Git, Docker, Jenkins, Postman, Webpack}
    \resumeSubItem{Cloud}{AWS, DigitalOcean, Firebase}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Africa International University}{Nairobi, Kenya}
      {Bachelor of Science in Information Technology (Part-Time)}{2022 -- Present}
    \resumeSubheading
      {Udemy}{Online}
      {The Complete Web Developer Bootcamp}{2023 -- 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Willsoft Technologies}{Nairobi, Kenya}
      {Fullstack Developer (Part-Time)}{Mar 2023 -- Present}
      \resumeItemListStart
        \resumeItem{E-commerce Platform Development}
          {Developed and deployed an end-to-end e-commerce platform using the MERN stack, providing features such as user account management, product browsing, cart management, and payment integration. Implemented the admin dashboard for inventory and order management, enhancing operational efficiency.}
        \resumeItem{API and Database Design}
          {Designed and integrated REST APIs for smooth communication between the frontend and backend, utilizing MongoDB for database management. Focused on scalability to support increasing traffic.}
        \resumeItem{Payment Gateway Integration}
          {Integrated third-party payment gateways such as PayPal, Stripe, and M-Pesa, ensuring secure and efficient transaction handling.}
        \resumeItem{CI/CD Integration}
          {Set up CI/CD pipelines using Jenkins and Docker for automated testing and deployment, reducing the release cycle time by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
      {XMpressa}{Remote}
      {Fullstack Developer (Part-Time)}{Jun 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Inventory Management System}
          {Contributed to the development of an inventory management system using the MERN stack, allowing businesses to track stock in real time and generate reports.}
        \resumeItem{API Design and Integration}
          {Designed RESTful APIs for frontend-backend interaction and integrated them into the system using MongoDB and Express.js.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{MERN Stack E-Commerce Platform}
      {Developed a full-stack e-commerce web application with features like user authentication, product browsing, cart management, and integrated payment processing. (2023)}
    \resumeSubItem{Inventory Management POS System}
      {Developed an inventory management POS system for a supermarket, featuring real-time tracking, reporting, and item management. (2024)}
    \resumeSubItem{Library Management System}
      {Created a MERN stack library management system with features like book categorization, user roles, and book borrowing functionality. (2024)}
    \resumeSubItem{Portfolio Website}
      {Built a personal portfolio website using React.js to showcase projects, skills, and experience. (2022)}
    \resumeSubItem{Real-Time Chat Application}
      {Developed a real-time chat application using Socket.io, Express, and React. Features included user authentication, private messaging, and notification systems. (2023)}
    \resumeSubItem{Task Management Application}
      {Built a task management app using React, Node.js, and MongoDB, enabling users to create, edit, and organize tasks with features like deadline reminders and project tracking. (2024)}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
